TGI Spinal Analysis Code

### 2022-12-14 analysis/tgi-spinal_analysis.Rmd
updating scatters

# correlation matrix
# plotting correlations between variables
corrplot(cormat, type = 'lower',
         p.mat = p, insig = "p-value", sig.level = -1,
         title = "VAS rating correlation matrix", 
         mar = c(0,0,1,0), 
         tl.cex=0.9) 
```
# Scatter plots
```{r scatter}
# Non TGI plots
ggplot(df_corr, aes(x = CNTcold, y =CNTwarm)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw() -> CNT_cw_plot

ggplot(df_corr, aes(x = CNTcold, y = CNTburn)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw() -> CNT_cb_plot

ggplot(df_corr, aes(x = CNTwarm, y = CNTburn)) +
  geom_point() +
  geom_smooth(method='lm') +
  theme_bw() -> CNT_wb_plot

# combine non TGI

>>>>

# correlation matrix
# plotting correlations between variables
corrplot(cormat, type = 'lower',
         p.mat = p, insig = "p-value", sig.level = -1,
         title = "VAS rating correlation matrix", 
         mar = c(0,0,1,0), 
         tl.cex=0.9) 
```
# Scatter plots
```{r scatter}
# Non TGI plots
ggplot(df_corr, aes(x = CNTcold, y =CNTwarm)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  labs(x = 'Cold Ratings', y = 'Warm Ratings') +
  xlim(0,100) + ylim(-15,100) +
  theme_bw() -> CNT_cw_plot

ggplot(df_corr, aes(x = CNTcold, y = CNTburn)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  labs(x = 'Cold Ratings', y = 'Burn Ratings') +
  xlim(0,100) + ylim(-15,100) +
  theme_bw() -> CNT_cb_plot

ggplot(df_corr, aes(x = CNTwarm, y = CNTburn)) +
  geom_smooth(method='lm', colour = 'black', alpha = .5) +
  geom_point(size = 1.5, shape = 21, colour = 'grey10', fill = 'grey60') +
  labs(x = 'Warm Ratings', y = 'Burn Ratings') +
  xlim(0,100) + ylim(-15,100) +
  theme_bw() -> CNT_wb_plot

# combine non TGI
CNT_corr_plot <- ggarrange(CNT_cw_plot, CNT_cb_plot, CNT_wb_plot,
                           nrow = 1, ncol = 3,
                           labels = c('A.','B.','C.'))
CNT_corr_plot <- annotate_figure(CNT_corr_plot, 
                                 top = text_grob("Non-TGI", 
                                                 size = 12))
CNT_corr_plot
